---
title: "Xtrategy"
subtitle: "Modelling Complexity for Efficient Planning"
#date: "`r Sys.Date()`"
fontsize: 20pt 
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: vignette

---


Do you have a lot of goals to achieve? 

Can't you decide which to focus on? Are your resources limited? 

Would you like to know which is the best set of goals to aim for and which actions do you need to achieve them?

Then... Xtrategy would help you with it.


## Styles

Currently `html_pretty` supports three page themes, `cayman` (the default),
`tactile`, and `architect`. And there are also two syntax highlight styles:
`github` to mimic the syntax highlight on Github, and `vignette` that is used by
`html_vignette`. If no highlight parameter is given, the default style created
by Pandoc will be used.

The theme and highlight styles can be given in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
```

## Happy Knitting!

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your package vignette.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can also include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](http://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.

